---
title: "Drug Metadata Improvement Tracking"
format: 
  html:
    embed-resources: true
    html-table-processing: none
    toc: true
---

```{r setup, include=FALSE}

library(argos)
library(srcr)
library(stringr)
library(dplyr)
library(tidyr)
library(RPostgres)
library(ggplot2)

pg_conn <- argos$new('pg_dq')$init_session(db_src =
                                             srcr::srcr(Sys.getenv('PEDSNET_BASE_CONFIG_NDQ')),
                                           base_dir = getwd(),
                                           cdm_schema = 'pedsnet_dcc_v62',
                                           results_schema = 'dqa_rox',
                                           vocabulary_schema = 'vocabulary',
                                           subdirs = list('specs' = 'specs_drugmeta',
                                                          'results' = 'results'),
                                           cdm = 'pedsnet',
                                           retain_intermediates = TRUE,
                                           cache_enabled = FALSE,
                                           results_name_tag = '')

set_argos_default(pg_conn)

prettify_ggplot <- function(){

    theme_bw() +
    theme(text = element_text(family = 'Montserrat',
                              size = 10),
          legend.title = element_text(family = 'Montserrat-Bold'))
  
}

uc_drug_plot <- function(dat){

  dat_pivot <- dat %>%
    select(site, check_description, database_version, unmapped_prop) %>%
    mutate(unmapped_prop = 1 - unmapped_prop) %>%
    pivot_wider(names_from = database_version,
                values_from = unmapped_prop)
  
  dat_pivot %>%
    ggplot() +
    geom_segment(aes(x = v61, xend = v62,
                     y = site, yend = site)) +
    geom_point(aes(x = v61, y = site), size = 2, color = '#8BBBB2') +
    geom_point(aes(x = v62, y = site), size = 2, color = '#945870') +
    facet_wrap(~check_description, labeller = label_wrap_gen()) +
    prettify_ggplot() +
    labs(y = 'Site',
         x = 'Prop. Populated')
} 


qd_metadata_plot <- function(dat,
                             dose = FALSE){
  
  if(dose){
    dat %>%
      filter(metadata_type == 'dose') %>%
      left_join(vocabulary_tbl('concept') %>%
                  select(concept_id, concept_name),
                by = c('dose_unit_concept_id' = 'concept_id')) %>%
      collect() %>%
      mutate(concept_name = ifelse(is.na(dose_unit_concept_id), 'NA', concept_name)) %>%
      group_by(site, concept_name) %>%
      slice_head(n = 1) %>%
      arrange(site, concept_name) %>%
      ggplot(aes(x = site)) +
      geom_boxplot(aes(ymin = min_val, lower = q1_val, middle = med_val, 
                       upper = q3_val, ymax = max_val,
                       group = interaction(concept_name, site)),
                   stat = 'identity') +
      facet_wrap(~concept_name) +
      prettify_ggplot() +
      coord_flip()
  }else{
    dat %>%
      filter(metadata_type != 'dose') %>%
      mutate(metadata_type = case_when(metadata_type == 'rx_length' ~ 
                                         'rx length in days \n(end date - start date)',
                                       TRUE ~ metadata_type)) %>%
      collect() %>%
      group_by(site, metadata_type) %>%
      slice_head(n = 1) %>%
      arrange(site, metadata_type) %>%
      ggplot(aes(x = site)) +
      geom_boxplot(aes(ymin = min_val, lower = q1_val, middle = med_val, 
                       upper = q3_val, ymax = max_val,
                       group = interaction(metadata_type, site)),
                   stat = 'identity') +
      facet_wrap(~metadata_type, scale = 'free_x') +
      prettify_ggplot() +
      coord_flip()
  }
  
}

qd_dat <- results_tbl('qd_example_drugs')

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

options(scipen = 999)

```

# Full Drug Table Assessment

## Population of Key Variables

```{r, fig.height=8}

uc_drug_plot(dat = results_tbl('uc_drug_metadata') %>% collect() %>%
               filter(!grepl('and|&', check_description)))

```

## Population of Key Variable Groups

These variables are often needed in combination in order to facilitate dose computation or to determine how long a patient was taking a medication.

```{r}

uc_drug_plot(dat = results_tbl('uc_drug_metadata') %>% collect() %>%
               filter(grepl('and|&', check_description)))

```

# Common Drug Assessment

## Albuterol

### Population of Key Variables
```{r, fig.height=8}

uc_drug_plot(dat = results_tbl('uc_example_drugs') %>% collect() %>%
               filter(!grepl('and|&', check_description),
                      drug_type == 'rx_albuterol'))

```

### Population of Key Variable Groups
```{r}

uc_drug_plot(dat = results_tbl('uc_example_drugs') %>% collect() %>%
               filter(grepl('and|&', check_description),
                      drug_type == 'rx_albuterol'))

```

### Value Plausibility
#### Dose by Unit
```{r, fig.height=7}

qd_metadata_plot(dat = qd_dat %>% filter(drug_type == 'rx_albuterol'),
                 dose = TRUE)

```

#### Metadata Distributions
```{r, fig.height=7}

qd_metadata_plot(dat = qd_dat %>% filter(drug_type == 'rx_albuterol'),
                 dose = FALSE)

```

## Amoxicillin

### Population of Key Variables
```{r, fig.height=8}

uc_drug_plot(dat = results_tbl('uc_example_drugs') %>% collect() %>%
               filter(!grepl('and|&', check_description),
                      drug_type == 'rx_amoxicillin_scdf'))

```

### Population of Key Variable Groups
```{r}

uc_drug_plot(dat = results_tbl('uc_example_drugs') %>% collect() %>%
               filter(grepl('and|&', check_description),
                      drug_type == 'rx_amoxicillin_scdf'))

```

### Value Plausibility
#### Dose by Unit
```{r, fig.height=7}

qd_metadata_plot(dat = qd_dat %>% filter(drug_type == 'rx_amoxicillin_scdf'),
                 dose = TRUE)

```

#### Metadata Distributions
```{r, fig.height=7}

qd_metadata_plot(dat = qd_dat %>% filter(drug_type == 'rx_amoxicillin_scdf'),
                 dose = FALSE)

```

## Bactrim

### Population of Key Variables
```{r, fig.height=8}

uc_drug_plot(dat = results_tbl('uc_example_drugs') %>% collect() %>%
               filter(!grepl('and|&', check_description),
                      drug_type == 'rx_bactrim'))

```

### Population of Key Variable Groups
```{r}

uc_drug_plot(dat = results_tbl('uc_example_drugs') %>% collect() %>%
               filter(grepl('and|&', check_description),
                      drug_type == 'rx_bactrim'))

```

### Value Plausibility
#### Dose by Unit
```{r, fig.height=7}

qd_metadata_plot(dat = qd_dat %>% filter(drug_type == 'rx_bactrim'),
                 dose = TRUE)

```

#### Metadata Distributions
```{r, fig.height=7}

qd_metadata_plot(dat = qd_dat %>% filter(drug_type == 'rx_bactrim'),
                 dose = FALSE)

```

## Fluoxetine (Prozac)

### Population of Key Variables
```{r, fig.height=8}

uc_drug_plot(dat = results_tbl('uc_example_drugs') %>% collect() %>%
               filter(!grepl('and|&', check_description),
                      drug_type == 'rx_fluoxetine_scdf'))

```

### Population of Key Variable Groups
```{r}

uc_drug_plot(dat = results_tbl('uc_example_drugs') %>% collect() %>%
               filter(grepl('and|&', check_description),
                      drug_type == 'rx_fluoxetine_scdf'))

```

### Value Plausibility
#### Dose by Unit
```{r, fig.height=7}

qd_metadata_plot(dat = qd_dat %>% filter(drug_type == 'rx_fluoxetine_scdf'),
                 dose = TRUE)

```

#### Metadata Distributions
```{r, fig.height=7}

qd_metadata_plot(dat = qd_dat %>% filter(drug_type == 'rx_fluoxetine_scdf'),
                 dose = FALSE)

```

## GLP1

### Population of Key Variables
```{r, fig.height=8}

uc_drug_plot(dat = results_tbl('uc_example_drugs') %>% collect() %>%
               filter(!grepl('and|&', check_description),
                      drug_type == 'rx_glp1ra_scdf'))

```

### Population of Key Variable Groups
```{r}

uc_drug_plot(dat = results_tbl('uc_example_drugs') %>% collect() %>%
               filter(grepl('and|&', check_description),
                      drug_type == 'rx_glp1ra_scdf'))

```

### Value Plausibility
#### Dose by Unit
```{r, fig.height=7}

qd_metadata_plot(dat = qd_dat %>% filter(drug_type == 'rx_glp1ra_scdf'),
                 dose = TRUE)

```

#### Metadata Distributions
```{r, fig.height=7}

qd_metadata_plot(dat = qd_dat %>% filter(drug_type == 'rx_glp1ra_scdf'),
                 dose = FALSE)

```

## Hydroxyurea

### Population of Key Variables
```{r, fig.height=8}

uc_drug_plot(dat = results_tbl('uc_example_drugs') %>% collect() %>%
               filter(!grepl('and|&', check_description),
                      drug_type == 'rx_hydroxyurea'))

```

### Population of Key Variable Groups
```{r}

uc_drug_plot(dat = results_tbl('uc_example_drugs') %>% collect() %>%
               filter(grepl('and|&', check_description),
                      drug_type == 'rx_hydroxyurea'))

```

### Value Plausibility
#### Dose by Unit
```{r, fig.height=7}

qd_metadata_plot(dat = qd_dat %>% filter(drug_type == 'rx_hydroxyurea'),
                 dose = TRUE)

```

#### Metadata Distributions
```{r, fig.height=7}

qd_metadata_plot(dat = qd_dat %>% filter(drug_type == 'rx_hydroxyurea'),
                 dose = FALSE)

```

## Insulin

### Population of Key Variables
```{r, fig.height=8}

uc_drug_plot(dat = results_tbl('uc_example_drugs') %>% collect() %>%
               filter(!grepl('and|&', check_description),
                      drug_type == 'insulin'))

```

### Population of Key Variable Groups
```{r}

uc_drug_plot(dat = results_tbl('uc_example_drugs') %>% collect() %>%
               filter(grepl('and|&', check_description),
                      drug_type == 'insulin'))

```

### Value Plausibility
#### Dose by Unit
```{r, fig.height=7}

qd_metadata_plot(dat = qd_dat %>% filter(drug_type == 'insulin'),
                 dose = TRUE)

```

#### Metadata Distributions
```{r, fig.height=7}

qd_metadata_plot(dat = qd_dat %>% filter(drug_type == 'insulin'),
                 dose = FALSE)

```

## Methylphenidate (Ritalin/Concerta)

### Population of Key Variables
```{r, fig.height=8}

uc_drug_plot(dat = results_tbl('uc_example_drugs') %>% collect() %>%
               filter(!grepl('and|&', check_description),
                      drug_type == 'rx_methylphenidate_scdf'))

```

### Population of Key Variable Groups
```{r}

uc_drug_plot(dat = results_tbl('uc_example_drugs') %>% collect() %>%
               filter(grepl('and|&', check_description),
                      drug_type == 'rx_methylphenidate_scdf'))

```

### Value Plausibility
#### Dose by Unit
```{r, fig.height=7}

qd_metadata_plot(dat = qd_dat %>% filter(drug_type == 'rx_methylphenidate_scdf'),
                 dose = TRUE)

```

#### Metadata Distributions
```{r, fig.height=7}

qd_metadata_plot(dat = qd_dat %>% filter(drug_type == 'rx_methylphenidate_scdf'),
                 dose = FALSE)

```

## Prednisone / Prednisolone

### Population of Key Variables
```{r, fig.height=8}

uc_drug_plot(dat = results_tbl('uc_example_drugs') %>% collect() %>%
               filter(!grepl('and|&', check_description),
                      drug_type == 'rx_predniso_lo_ne_scdf'))

```

### Population of Key Variable Groups
```{r}

uc_drug_plot(dat = results_tbl('uc_example_drugs') %>% collect() %>%
               filter(grepl('and|&', check_description),
                      drug_type == 'rx_predniso_lo_ne_scdf'))

```

### Value Plausibility
#### Dose by Unit
```{r, fig.height=7}

qd_metadata_plot(dat = qd_dat %>% filter(drug_type == 'rx_predniso_lo_ne_scdf'),
                 dose = TRUE)

```

#### Metadata Distributions
```{r, fig.height=7}

qd_metadata_plot(dat = qd_dat %>% filter(drug_type == 'rx_predniso_lo_ne_scdf'),
                 dose = FALSE)

```

## RAASi

### Population of Key Variables
```{r, fig.height=8}

uc_drug_plot(dat = results_tbl('uc_example_drugs') %>% collect() %>%
               filter(!grepl('and|&', check_description),
                      drug_type == 'rx_raasi'))

```

### Population of Key Variable Groups
```{r}

uc_drug_plot(dat = results_tbl('uc_example_drugs') %>% collect() %>%
               filter(grepl('and|&', check_description),
                      drug_type == 'rx_raasi'))

```

### Value Plausibility
#### Dose by Unit
```{r, fig.height=7}

qd_metadata_plot(dat = qd_dat %>% filter(drug_type == 'rx_raasi'),
                 dose = TRUE)

```

#### Metadata Distributions
```{r, fig.height=7}

qd_metadata_plot(dat = qd_dat %>% filter(drug_type == 'rx_raasi'),
                 dose = FALSE)

```
